Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-06 SupportingInformation.Rmd
I fixed a bug (I think) that was preventing knitting

```{r read_BMR_birds_and_copulaplot, echo=F, results='hide'}
set.seed(seed)
raw_b<-readxl::read_xls("./Data/BMR/BirdBodyMassesMetabolicRates/BirdMassesAndMetabolicRatesMcNab2008.xls")
raw_b<-raw_b[,1:3]
raw_b<-na.omit(raw_b)
raw_b<-raw_b[,2:3]
raw_b<-as.data.frame(raw_b)

@@

>>>>

```{r read_BMR_birds_and_copulaplot, echo=F, results='hide'}
library(readxl)
set.seed(seed)
raw_b<-readxl::read_xls("./Data/BMR/BirdBodyMassesMetabolicRates/BirdMassesAndMetabolicRatesMcNab2008.xls")
raw_b<-raw_b[,1:3]
raw_b<-na.omit(raw_b)
raw_b<-raw_b[,2:3]
raw_b<-as.data.frame(raw_b)

@@

    saveRDS(myres,paste(resloc,"ricker_SJ_kend.RDS",sep=""))
  }
 }
}
```
